\begin{thebibliography}{1}

\bibitem{GameEngineArchitecture}
J. Gregory, Game Engine Architecture. 3rd ed. USA: CRC Press, 2019.

\bibitem{MendezBaudryMonperrus}
D. Mendez, B. Baudry, M. Monperrus, Empirical Evidence of Large-Scale Diversity in API Usage of Object-Oriented Software, in International Conference on Source Code Analysis and Manipulation, Eindhoven, 2013, pp. 10, 10.1109/SCAM.2013.6648183.

\bibitem{Bierhoff}
K. Bierhoff, "API Protocol Compliance in Object-Oriented Software," Ph.D. dissertation, Institute for Software Research, School of Computer Science, Carnegie Mellon University, Pittsburgh, 2009.

\bibitem{Simsek}
B. Simsek, "How To Create Program Libraries," Aug 18 2004.

\bibitem{FrameworkDesign}
D. Riehle, "Framework Design: A Role Modeling Approach," ETH Zürich, Dissertation Nr. 13509, 2000.
 
\bibitem{3DGameEngineArchitecture} 
D. Eberly, 3D Game Engine Architecture: Engineering Real-Time Applications with Wild Magic, USA: Elsevier Inc, 2005.

\bibitem{AnIntroductionToComputerGraphicsForArtists}
A. Paquette, An Introduction to Computer Graphics for Artists, 2nd ed. London: Springer, 2013.

\bibitem{FPSGames}
GamesRadar+ (2018) The 25 best FPS game of all time. [Online]. Available: https://www.gamesradar.com/best-fps-games/3/

\bibitem{AIGameEngineProgramming}
B. Schwab, AI Game Engine Programming, 2nd ed. Boston, 2009. 

\bibitem{RacingGames}
Ranker (2019) The 20+ Most Popular Racing Games in 2019. [Online]. Available: https://www.ranker.com/list/most-popular-racing-video-games-today/ranker-games

\bibitem{SearchingForTheOptimalRacingLineUsingGeneticAlgorithms}
L. Cardamone, D. Loiacono, P. L. Lanzi and A. P. Bardelli. "Searching for the Optimal Racing Line Using Genetic Algorithms," in Computational Intelligence and Games, 2010, doi. 388 - 394. 10.1109/ITW.2010.5593330. 

\bibitem{FundamentalsOfGameDesign}
E. Adams, Fundamentals of Game Design, 2nd ed. Berkeley, 2010

\bibitem{FightingGames}
Game Informer (2019) The 30 Greatest Fighting Games of All Time. [Online]. Available: https://www.gameinformer.com/2019/04/25/the-30-greatest-fighting-games-of-all-time

\bibitem{BeetEmUpGames}
PC Gamer (2018) The best beat-em-ups on PC. [Online]. Available: https://www.pcgamer.com/best-beat-em-up-games/

\bibitem{PlatformGames}
PCGamesN (2019) The best platform games on PC. [Online]. Available: https://www.pcgamesn.com/best-platform-games

\bibitem{UnityHeightMap}
Unity (2020) Manual: Heightmap. [Online]. Available: https://docs.unity3d.com/Manual/StandardShaderMaterialPara
meterHeightMap.html

\bibitem{StrategyGames}
PC Gamer (2019) Best Strategy Games on PC. [Online]. Available: https://www.pcgamer.com/the-best-strategy-games/

\bibitem{HeightmapRenderingUsingAFloorcastingAlgorithm}
Observable (2018) Heightmap rendering using a floorcasting algorithm. [Online]. Available: https://observablehq.com/@ehouais/heightmap-rendering-using-a-floorcasting-algorithm

\bibitem{MMOGames}
MMORPG (2019) MMORPG Game List 2019. [Online]. Available: https://www.mmorpg.com/games-list

\bibitem{BattleRoyaleGames}
PC Gamer (2019) The Battle Royale Games of 2019. [Online]. Available: https://www.pcgamer.com/battle-royale-games-2018/

\bibitem{Freemium}
Business Dictionary (2019) What is freemium? Definition and meaning. [Online]. Available: http://www.businessdictionary.com/definition/freemium.html

\bibitem{ItchIoAbout}
Itch.io (2019) About itch.io. [Online]. Available: https://itch.io/docs/general/about

\bibitem{ItchIoEngines}
Itch.io (2019) Most used Engines. [Online]. Available: https://itch.io/game-development/engines/most-projects

\bibitem{Scripting}
R. P. Loui, "In Praise of Scripting: Real Programming Pragmatism," [Online], Jan, 10, 2012, Available: https://steloflute.tistory.com/389

\bibitem{Boo}
Mono (2017) Boo [Online]. Available: https://www.mono-project.com/archived/boo/

\bibitem{UnityScript}
J. Suvak, Learn Unity3D Programming with UnityScript: Unity’s JavaScript for Beginners, USA: Apress, 2014.

\bibitem{UnityGames}
Unity (2019) Made With Unity. [Online]. Available: https://unity.com/madewith

\bibitem{UnrealAbout}
Unreal Engine (2019) Features. [Online]. Available: https://www.unrealengine.com/en-US/features

\bibitem{UnrealGames}
Techtudo (2011) Top 10: \textit{O mais belos games com} Unreal Engine 3 [Online]. Available: https://www.techtudo.com.br/noticias/noticia/2011/02/top-10-o-mais-belos-games-com-unreal-engine-3.html

\bibitem{NvidiaAbout}
NVidia (2019) Company Overview. [Online]. Available: https://www.nvidia.com/en-us/drivers/citizenship-report-company-overview/

\bibitem{CryEngineAbout}
CRYENGINE (2019) Features. [Online]. Available: https://www.cryengine.com/features

\bibitem{CryEngineGames}
CryEngine (2019) All the games created by video game developer Crytek. [Online]. Available: https://www.crytek.com/games>

\bibitem{OpenSource}
A. M. Laurent, Understanding Open Source and Free Software Licensing, USA: O'Reilly Media, 2004.

\bibitem{MIT}
Choose a License (2019) Choose an open source license. [Online]. Available: https://choosealicense.com/

\bibitem{GDScript}
Godot Engine. (2018) GDScript the Godot Engine lastest documentation. [Online]. Available: http://docs.godotengine.org/en/3.0/getting\_started/scripting
/gdscript/gdscript\_basics.html

\bibitem{GodotAbout}
OpenHub (2019) The Godot Game Engine Open Source Project on Open Hub. [Online]. Available: https://www.openhub.net/p/godotengine

\bibitem{GodotGames}
Godot Engine (2019) Showcase. [Online]. Available: https://godotengine.org/showcase

\bibitem{GameMakerDragNDrop}
YoYoGames (2019) Drag And Drop Overview. [Online]. Available: https://docs2.yoyogames.com/source/\_build/3\_scripting/1\_drag
\_and\_drop\_overview/index.html

\bibitem{GML}
YoYoGames (2019) GLM Overview. [Online]. Available: https://docs.yoyogames.com/source/dadiospice/002\_reference
/001\_gml\%20language\%20overview/

\bibitem{TheGameMakerStandard}
D. V. Vinciguerra and A. Howell, The GameMaker Standard. USA: CRC Press, 2016.

\bibitem{GameMaker}
YoYoGames (2019) GameMaker. [Online]. Available: https://www.yoyogames.com/gamemaker

\bibitem{PlutoGitHub}
GitHub (2019) pluto. [Online]. Available: https://github.com/felipegodias/pluto

\bibitem{GLM}
GitHub (2019) OpenGL Mathematics. [Online]. Available: https://github.com/g-truc/glm

\bibitem{GLEW}
GitHub (2019) The OpenGL Extension Wrangler Library. [Online]. Available: https://github.com/nigels-com/glew

\bibitem{GLFW}
GitHub (2019) A multi-platform library for OpenGL, OpenGL ES, Vulkan, window and input. [Online]. Available: https://github.com/glfw/glfw

\bibitem{fmt}
GitHub (2019) A modern formatting library. [Online]. Available: https://github.com/fmtlib/fmt

\bibitem{spdlog}
GitHub (2019) Fast C++ logging library. [Online]. Available: https://github.com/gabime/spdlog

\bibitem{boost}
GitHub (2019) Super-project for modularized Boost. [Online]. Available: https://github.com/boostorg/boost

\bibitem{yaml-cpp}
GitHub (2019) A YAML parser and emitter in C++. [Online]. Available: https://github.com/jbeder/yaml-cpp

\bibitem{stb}
GitHub (2019) stb single-file public domain libraries for C/C++. [Online]. Available: https://github.com/nothings/stb

\bibitem{Box2DAbout}
Box2D (2019) About. [Online]. Available: https://box2d.org/about/

\bibitem{conan}
Conan (2019) C/C++ Open Source Package Manager. [Online]. Available: https://conan.io/

\bibitem{CMake}
CMake (2019) CMake. [Online]. Available: https://cmake.org/

\bibitem{TheCaseForResearchInGameEngineArchitecture}
E. F. Anderson, "The Case for Research in Game Engine Architecture," 2018, Available: http://eprints.bournemouth.ac.uk/24322/1/FP8GEA.pdf

\bibitem{Malloc}
CPP Reference (2018) std::malloc [Online]. Available: https://en.cppreference.com/w/cpp/memory/c/malloc

\bibitem{MemoryAllocationPatternsUsedInGameDevelopment}
Stack Exchange (2012) Memory allocation patterns used in game development [Online]. Available: https://gamedev.stackexchange.com/questions/25782/memory-allocation-patterns-used-in-game-development

\bibitem{GangOfFour}
E. Gamma, R. Helm, R. Johnson and R. Vlissides, Design Patterns: Elements of Reusable Object-Oriented Software. USA: Addison-Wesley, 1994.

\bibitem{GameProgrammingPatterns}
R. Nystrom, Game Programming Patterns, USA: Genever Benning, 2014

\bibitem{DependencyInjectionIn.NET}
M. Seemann, Dependency Injection in .NET, New York: Manning Publications Co, 2012

\bibitem{SystemsAndSoftwareEngineeringVocabulary}
Systems and software engineering — Vocabulary, ISO/IEC/IEEE 24765, 2010.

\bibitem{ZenjectSignals}
GitHub (2019) Zenject Signals. [Online]. Available: https://github.com/modesttree/Zenject/blob/master
/Documentation/Signals.md

\bibitem{pub-sub}
Toptal (2014) The Publish-Subscribe Pattern on Rails. [Online]. Available: https://www.toptal.com/ruby-on-rails/the-publish-subscribe-pattern-on-rails

\bibitem{DeadZones}
Third Helix (2013) DOING THUMBSTICK DEAD ZONES RIGHT. [Online]. Available: http://www.third-helix.com/2013/04/12/doing-thumbstick-dead-zones-right.html

\bibitem{LearnOpenGL}
LearnOpenGL (2019) Materials. [Online]. Available: https://learnopengl.com/Lighting/Materials

\bibitem{OpenGLBible}
R. S. Wright, Jr, B. Lipchak and N. Haemel, OpenGL® SUPERBIBLE: comprehensive tutorial and reference, 4th ed. Boston: Addison-Wesley, 2007.

\bibitem{UnityResources}
Unity (2019) Assets, Resources and AssetBundles. [Online]. Available: https://learn.unity.com/tutorial/assets-resources-and-assetbundles

\bibitem{ObjectOrientedGameProgrammingTheSceneSystem}
Riverman Media (2019) Object-Oriented Game Programming: The Scene System. [Online]. Available: https://rivermanmedia.com/object-oriented-game-programming-the-scene-system/

\bibitem{ObjectOrientedSceneManagement}
gamedev.net (2002) Object-Oriented Scene Management. [Online]. Available: https://www.gamedev.net/articles/programming/general-and-gameplay-programming/object-oriented-scene-management-r1812/

\bibitem{SceneGraphRepresentationAndLearning}
Stanford (2019) Scene Graph Representation and Learning. [Online]. Available: https://cs.stanford.edu/people/ranjaykrishna/sgrl/index.html

\bibitem{3DGameEngineDesign}
D. H. Eberly, 3D Game Engine Design: A Practical Approach to Real-Time Computer Graphics, 2nd ed. Oxford: Elsevier, 2007.

\bibitem{DesigningAModernRenderingEngine}
M. Bauchinger, "Designing a Modern Rendering Engine," Bs. dissertation, Institut fur Computergraphik und Algorithmen der Technischen Universit., Wien, 2007.

\bibitem{DirectX}
F. D. Luna, Introduction to 3D Game Programming With DirectX® 12, Dulles: David	Pallai, 2016.

\bibitem{Metal}
J. Clayton, Metal Programming Guide: Comprehensive Tutorial and Reference via Swift, USA: Pearson Higher, 2017. 

\bibitem{AMeshDataStructureForRenderingAndSubdivision}
R. F. Tobler, S. Maierhofer, "A Mesh Data Structure for Rendering and Subdivision", UNION Agency – Science Press [Online], Feb 3 2006. Available: http://wscg.zcu.cz/wscg2006/Papers\_2006/Short/E17-full.pdf 

\bibitem{UnityDrawCall}
Unity (2019) Draw call batching. [Online]. Available: https://docs.unity3d.com/Manual/DrawCallBatching.html

\bibitem{GamePhysicsEngineDevelopment}
I. Millington, Game Physics Engine Development: How to Build a Robust Commercial-Grade Physics Engine for Your Game, 2nd ed. Burlington: Elsevier, 2010.

\bibitem{PhysXAbout}
NVidia (2019) PhysX SDK. [Online]. Available: https://developer.nvidia.com/physx-sdk/

\bibitem{HavokAbout}
Havok (2019) Products. [Online]. Available: https://www.havok.com/products/

\bibitem{PhysicsForGameDevelopers}
D. M. Bourg and B. Bywalec, Physics for Game Developers, 2nd ed. USA: O’Reilly Media, 2013.

\bibitem{FlappyBird}
AmongTech (2014) Could Flappy Bird beat Candy Crush as the most popular Mobile Game of 2014? [Online]. Available: https://www.amongtech.com/could-flappy-bird-beat-candy-crush-as-the-most-popular-mobile-game-of-2014/

\bibitem{Mono}
Mono (2019) Home [Online]. Available: https://www.mono-project.com/

\bibitem{IL2CPP}
Unity (2019) IL2CPP [Online]. Available: https://docs.unity3d.com/Manual/IL2CPP.html

\bibitem{ComparisonBetweenFamousGameEnginesAndEminentGames}
P. Mishra and U. Shrawankar. "Comparison between Famous Game Engines and Eminent Games," Special Issue on Artificial Intelligence Underpinning, vol. 4, doi. 10.9781/ijimai.2016.4113, Jan 2016.

%\bibitem{OverviewAndComparativeAnalysisOfGameEnginesForDesktopAndMobileDevice} 
%ELEFTHERIA CHRISTOPOULOU, STELIOS XINOGALOS. Overview and Comparative Analysis of Game Engines for Desktop and Mobile Devices. International Journal of Serious Games. Volume 4, Fascículo 4, Páginas 21-36, Dezembro 2017.

%\bibitem{GameProgrammingAlgorithmsAndTechniques}
%ADHAV, Sanjay.  Game Programming Algorithms and Techniques: A Platform-Agnostic Approach. Primeira Edição. Estados Unidos: Addison-Wesley, 2013.

%\bibitem{MathematicsForComputerGraphics}
%VINCE, John. Mathematics for Computer Graphics. Segunda Edição. Inglaterra: Springer, 2006.

%\bibitem{GraphicsShadersTheoryAndPractice} 
%BAILEY, Mike. CUNNINGHAM, Steve. Graphics Shaders: Theory and Practice. Segunda Edição. Estados Unidos: CRC Press, 2011.











\end{thebibliography}