\subsubsection{Pluto}\label{sec:pluto}
Pluto\cite{PlutoGitHub} is an open-source game engine developed by me and focuses on 2D games. In the section \ref{sec:game-egnine-architecture} is described how some of the systems that are already implemented in Pluto works. Pluto was developed using C++ as main language and is currently using a lot of third parties libraries to help the development process, the currently using libraries are OpenGL Mathematics\footnote{"OpenGL Mathematics (GLM) is a header only C++ mathematics library for graphics software based on the OpenGL Shading Language (GLSL) specifications."\cite{GLM}}, GLEW\footnote{"The OpenGL Extension Wrangler Library (GLEW) is a cross-platform open-source C/C++ extension loading library. GLEW provides efficient run-time mechanisms for determining which OpenGL extensions are supported on the target platform. OpenGL core and extension functionality is exposed in a single header file. GLEW has been tested on a variety of operating systems, including Windows, Linux, Mac OS X, FreeBSD, Irix, and Solaris."\cite{GLEW}}, GLFW\footnote{"GLFW is an Open Source, multi-platform library for OpenGL, OpenGL ES and Vulkan application development. It provides a simple, platform-independent API for creating windows, contexts and surfaces, reading input, handling events, etc."\cite{GLFW}}, \{fmt\}\footnote{"\{fmt\} is an open-source formatting library for C++. It can be used as a safe and fast alternative to (s)printf and iostreams."\cite{fmt}}, spdlog\footnote{"Very fast, header-only/compiled, C++ logging library."\cite{spdlog}}, Boost\footnote{"The Boost project provides free peer-reviewed portable C++ source libraries."\cite{boost}}, yaml-cpp\footnote{"yaml-cpp is a YAML parser and emitter in C++ matching the YAML 1.2 spec."\cite{yaml-cpp}}, stb\footnote{"single-file public domain (or MIT licensed) libraries for C/C++"\cite{stb}}, Box2D\footnote{"Box2D is an open source C++ engine for simulating rigid bodies in 2D. Box2D is developed by Erin Catto and has the zlib license."\cite{Box2DAbout}}, Conan\footnote{"The open source, decentralized and multi-platform package manager to create and share all your native binaries."\cite{conan}} and CMake\footnote{"CMake is an open-source, cross-platform family of tools designed to build, test and package software. CMake is used to control the software compilation process using simple platform and compiler independent configuration files, and generate native makefiles and workspaces that can be used in the compiler environment of your choice."\cite{CMake}}. Pluto has support for create 2D games with real-time physics simulation, in this article is shown a game that was developed using Pluto as game engine, a screenshot of the game can be seen in figure \ref{fig:pluto-flappy-bird}. Pluto is still a young project, not much more than half a year but is already in a stable state. Some of the features that Pluto already supports are file management, run-time asset loading (e.g. textures, meshes, materials, shaders, fonts and texts), 3D rendering, text rendering, real-time 2D physics, logging, external configuration loading, input management and 3D math library. In near future, the following features will be added to Pluto in the given order: compressed assets packages, python scripting support, audio player, visual editor and UI Manager. Pluto was only tested in Microsoft Windows but the project was designed to work both in Linux and Mac OS X as well.